Oral Manuscript

### 2018-08-03 08-SCPME-Simulations.Rmd
updated material with new vignettes

@@

@@

 - `shrinkXY` = shrinking characteristics regression estimator with A = X, B = cov(X, Y), and C = Y (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$)

 - `shrinkXYO` = shrinking characteristics regression estimator meant to emulate the "likelihood" for $\beta$ (using oracle $\Omega_{y | x}^{*}$) (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$)

@@

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150)
 - `r` = c(1, 5)
 - `sparse` = 0.5
 - `sigma` = "tridiag"

@@

## Plots

@@

# load data
load("images/sim5.Rdata")

@@

# MSPE by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 500, sparse = 0.5, sigma = tridiag)")

@@

# MSPE by P (N = 100, R = 1, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, R == 1, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 1, sparse = 0.5, sigma = tridiag)")

@@

**Notable: N = 100, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**

@@

# MSPE table (N = 100, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

@@

# MSPE by P (N = 100, R = 5, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, R == 5, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 5, sparse = 0.5, sigma = tridiag)")

**Notable: N = 100, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**

# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

# MSPE by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 5000, sparse = 0.5, sigma = tridiag)")

# MSPE by P (N = 1000, R = 1, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, R == 1, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 1, sparse = 0.5, sigma = tridiag)")

**Notable: N = 1000, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**

# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 1)
data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

# MSPE by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 5, sparse = 0.5, sigma = tridiag)")

@@

# MSPE table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

@@

## Takeaways

1. `shrinkBO` (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$. I don't think it's surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.

2. It's interesting to see that in all cases `shrinkBS` (penalty: $\lambda\left\| \Omega\Sigma_{xy}^{*} \right\|_{1}$) performed worse than `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$). So the takeaway is that for these two very similar estimators, the estimator with the oracle $\Sigma_{xy}$ cross-covariance matrix performs much worse than using the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$. Is this due to an error? Could the root cause be because I centered the data?

3. `OracleO` ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$) performed awful in all simulations as well... possibly link to the Abundant paper?

4. `shrinkXY` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$) and `shrinkXYO` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$) did not perform well relative to the others in the high-dimensional setting. In the low-dimensional setting, they performed better but worse than `lasso` and `ridge`. But what is an appropriate data generating model for these estimators? A model that can perfectly fit the observed values? And would MSPE be the most appropriate criteria for these estimators?

@@

## Questions

1. Is MSPE the best criteria? Or would model error be a better metric?

>>>>

## Estimator Comparison

@@

 - `oracleS` = oracle estimator with the true $\Sigma_{xy}^{*}$ known and sample estimator for $\Omega$ ($\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}$)

@@

@@

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag")

@@

### Plots

#### High Dimension

Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE). Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.

@@

# load data
load("images/sim6.Rdata")

@@

# ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")

@@

# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")

@@

**Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = "tridiag"**

@@

# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

#### Low Dimension

# ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")

@@

# ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")

@@

# ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

@@

### Takeaways

1. In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$. It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.

2. In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS. The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.

3. When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.

4. It is interesting that `oracleO` performed worse than `oracleS` in the final table. It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.

@@

## Shrinking Covariance

We compare the performance of the `shrinkB` and `shrinkBO` estimators when manually shrinking the sample covariance matrix of $X$ and $Y$ (denoted $\Sigma_{xy}$). Each data scenario was replicated a total of 20 times.

For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$. We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150, 200)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag", "compound")

### Plots

# load data
load("images/sigma.Rdata")

# design color palette
bluetowhite <- c("#000E29", "white")

# change to numeric
data$lam %<>% as.character %>% as.numeric
data$const %<>% as.character %>% as.numeric

#### High Dimension

##### `shrinkB`

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

##### `shrinkBO`

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

#### Low Dimension

##### `shrinkB`

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

#### `shrinkBO`

# shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

# shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

### Takeaways

1. In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE. This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.

2. In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.

3. The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.

4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)

### 2018-08-03 index.Rmd
updated material with new vignettes

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [lib.bib, packages.bib]
bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: no
lof: no
fontsize: 11pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

@@

# ```{r include=FALSE}
# # automatically create a bib database for R packages
# knitr::write_bib(c(
#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
# ), 'packages.bib')
# ```

>>>>

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::pdf_book:
    toc_depth: 2
  bookdown::gitbook:
    fig_caption: false
documentclass: book
bibliography: [lib.bib, packages.bib]
#bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: no
lof: no
fontsize: 11pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

@@

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), "glasso", "ADMMsigma"), 'packages.bib')
